CODECHECK: An Open Science initiative for the independent execution of computations underlying research articles during peer review improves reproducibility

### 2021-02-09 codecheck-paper.tex
switch CI to latex image

We use freely available infrastructure, GitHub and Zenodo, to run our
system.  The \texttt{codecheckers} \textbf{GitHub}
organisation at \url{https://github.com/codecheckers} contains
projects for managing the project website, the codecheckers community
and its discussions, code repositories, and the main register of
CODECHECKs. Both the project website \url{https://codecheck.org.uk/}}
and the register at \url{https://codecheck.org.uk/register}
are hosted as GitHub pages.
The register database is a single table in CSV format that connects the
certificate identifier with the repository associated with a specific
conducted CODECHECK. Each of these repositories, which currently can
be hosted on GitHub or Open Science Framework (OSF), contains the
CODECHECK metadata file \texttt{codecheck.yml}. The register further
contains a column for the type of check, e.g.,~community, journal, or
conference, and the respective GitHub issue where communications and
assignments around a specific check are organised. No information is
duplicated between the register and the metadata files. The continuous
integration infrastructure of GitHub, GitHub Actions, is used to
automate the register for viewing (HTML) and for integration with
other services (CSV, JSON).  \textbf{Zenodo} is our preferred open repository for
storing certificates. It mints DOIs for deposits and ensures
long-term availability of all digital artefacts related to the
project. The CODECHECK community on Zenodo is available at
\url{https://zenodo.org/communities/codecheck/}. It holds
certificates, the regularly archived register
\cite{codecheck_register_jan2021}, and other material related to
CODECHECK.

@@

Repository: Daniel Nüst, Stephen Eglen, & Iain Davies. (2021). codecheckers/register: CODECHECK Register Deposit January 2021 (Version 2021-01) [Data set]. Zenodo. http://doi.org/10.5281/zenodo.4486559

>>>>

We use freely available infrastructure, GitHub and Zenodo, to run our
system.  The \texttt{codecheckers} \textbf{GitHub}
organisation at \url{https://github.com/codecheckers} contains
projects for managing the project website, the codecheckers community
and its discussions, code repositories, and the main register of
CODECHECKs. Both the project website \url{https://codecheck.org.uk/}
and the register at \url{https://codecheck.org.uk/register}
are hosted as GitHub pages.
The register database is a single table in CSV format that connects the
certificate identifier with the repository associated with a specific
conducted CODECHECK. Each of these repositories, which currently can
be hosted on GitHub or Open Science Framework (OSF), contains the
CODECHECK metadata file \texttt{codecheck.yml}. The register further
contains a column for the type of check, e.g.,~community, journal, or
conference, and the respective GitHub issue where communications and
assignments around a specific check are organised. No information is
duplicated between the register and the metadata files. The continuous
integration infrastructure of GitHub, GitHub Actions, is used to
automate the register for viewing (HTML) and for integration with
other services (CSV, JSON).  \textbf{Zenodo} is our preferred open repository for
storing certificates. It mints DOIs for deposits and ensures
long-term availability of all digital artefacts related to the
project. The CODECHECK community on Zenodo is available at
\url{https://zenodo.org/communities/codecheck/}. It holds
certificates, the regularly archived register
\cite{codecheck_register_jan2021}, and other material related to
CODECHECK.

@@

Repository: Daniel Nüst, Stephen Eglen, \& Iain Davies. (2021). codecheckers/register: CODECHECK Register Deposit January 2021 (Version 2021-01) [Data set]. Zenodo. http://doi.org/10.5281/zenodo.4486559
